\textit{Supplementary materials for}: Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-02 paper/main.tex
recomputing fingerprints after (hopefully) fixing quail "bug"
note: the "bug" was an edge case related to computing permutation-corrected clustering scores.  in the previous implementation, if all list items had the same feature value for a given feature, the corrected clustering score for that feature would be 1, since the comparisons for permuted vs. observed scores were made using a strictly "less than" comparison (and none of the permuted scores would be greater than the observed score).

to fix this edge case, quail now considers 3 cases for each permuted score (and computed the average a

\caption{\textbf{Memory ``fingerprints'' (order manipulation conditions).} The
across-participant distributions of clustering scores for each feature type
($x$-coordinate) are displayed for each experimental condition (color),
separately for order manipulation (early, top) and randomly ordered (late,
bottom) lists. See Figures~\fingerprintsRandom~and~\fingerprintsAdaptive~for
analogous plots for the random and adaptive conditions.}
\label{fig:fingerprints}

@@

\caption{\textbf{Recall probability and clustering scores on early and late
lists.} The bar heights display the average (across participants) recall
probabilities (\textbf{A.}), temporal clustering scores (\textbf{B.}), and
feature clustering scores (\textbf{C.}) for early (gray) and late (gold) lists.
For the feature rich bars (left), the feature clustering scores are averaged
across features. For the order manipulation conditions, feature clustering
scores are displayed for the focused-on feature for each condition (e.g.,
category clustering scores are displayed for the category condition, and so
on). All panels: error bars denote bootstrap-estimated 95\% confidence
intervals. The horizontal dotted lines denote the average values (across all
lists and participants) for the feature rich condition.
\textbf} \label{fig:barplots}

>>>>

\caption{\textbf{Memory ``fingerprints'' (order manipulation conditions).} The
across-participant clustering scores for each feature type ($x$-coordinate) are
displayed for each experimental condition (color), separately for order
manipulation (early, top) and randomly ordered (late, bottom) lists. Error bars
denote bootstrap-estimated 95\% confidence intervals. See
Figures~\fingerprintsRandom~and~\fingerprintsAdaptive~for analogous plots for
the random and adaptive conditions.} \label{fig:fingerprints}

@@

\caption{\textbf{Recall probability and clustering scores on early and late
lists.} The bar heights display the average (across participants) recall
probabilities (\textbf{A.}), temporal clustering scores (\textbf{B.}), feature
clustering scores (\textbf{C.}), and residual feature clustering scores (after
factoring out temporal clustering effects; \textbf{D.}) for early (gray) and
late (gold) lists. For the feature rich bars (left), the feature clustering
scores are averaged across features. For the order manipulation conditions,
feature clustering scores are displayed for the focused-on feature for each
condition (e.g., category clustering scores are displayed for the category
condition, and so on). All panels: error bars denote bootstrap-estimated 95\%
confidence intervals. The horizontal dotted lines denote the average values
(across all lists and participants) for the feature rich condition. The bars
denote $t$-tests between the corresponding bars, and the asterisks denote the
Benjamini-Hochberg-corrected $p$-values. Comparisons for which corrected $p
\geq 0.05$ are not shown.} \label{fig:barplots}

### 2023-11-02 paper/supplement.tex
recomputing fingerprints after (hopefully) fixing quail "bug"
note: the "bug" was an edge case related to computing permutation-corrected clustering scores.  in the previous implementation, if all list items had the same feature value for a given feature, the corrected clustering score for that feature would be 1, since the comparisons for permuted vs. observed scores were made using a strictly "less than" comparison (and none of the permuted scores would be greater than the observed score).

to fix this edge case, quail now considers 3 cases for each permuted score (and computed the average a

    \caption{\textbf{Memory ``fingerprints'' (random conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-axis) are displayed for each experimental condition
    (color), separately for early (top) and late (bottom) lists.}
        \label{fig:fingerprints-random}
\end{figure}

@@

    \caption{\textbf{Memory ``fingerprints'' (adaptive conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-axis) are displayed for each experimental condition
    (color).}
        \label{fig:fingerprints-adaptive}
\end{figure}

>>>>

\caption{\textbf{Memory ``fingerprints'' (random conditions).} The
across-participant clustering scores for each feature type ($x$-axis) are
displayed for each experimental condition (color), separately for early (top)
and late (bottom) lists. Error bars denote bootstrap-estimated 95\% confidence
intervals.}

\label{fig:fingerprints-random} \end{figure}

@@

\caption{\textbf{Memory ``fingerprints'' (adaptive conditions).} The
across-participant clustering scores for each feature type ($x$-axis) are
displayed for each experimental condition (color). Error bars denote
bootstrap-estimated 95\% confidence intervals.}

\label{fig:fingerprints-adaptive} \end{figure}
